---
title: "Market Basket Analysis"
author: "Prerit Anwekar"
date: "March 27, 2016"
output: pdf_document
---
Install Libraries
```{r}
install.packages("dplyr") #For manupalating datasets efficiently.
install.packages("gtools") #A package for Combinatorial calculations.
install.packages("plyr")
install.packages("tidyr")
install.packages("ggplot2")
```
Load Libraries
```{r}
library(plyr);library(dplyr);library(tidyr)
library(gtools)
library(ggplot2)
```
Global Variables
```{r}
number_of_candidate_itemset<-c()
number_of_frequent_itemset<-c()

tracking.statistics.table.fkf1<-c()
tracking.statistics.table.fkfk<-c()

data.mb<-c()
nursery.b<-c()
car.b<-c()
mushroom.b<-c()

Toy.fqi1<-c()
Toy.fqi2<-c()
Toy.fqi3<-c()

Nursery.fqi1<-c()
Nursery.fqi2<-c()
Nursery.fqi3<-c()

Car.fqi1<-c()
Car.fqi2<-c()
Car.fqi3<-c()

Tictac.fqi1<-c()
Tictac.fqi2<-c()
Tictac.fqi3<-c()

rules.conf.table<-data.frame()
rules.lift.table<-data.frame()

countRules<- 0
bruteForce<- 0

conf.brute.tables<- data.frame()
max.cl.tables<-data.frame()
close.freq.table<-data.frame()
```
Binarize Datasets
```{r}
binarize<-function(dataset,names){ 
  drops<-NA
  colnames(dataset)<- paste("{",names,"}:",sep = "")
  dataset<-dataset[,!(names(dataset)%in%drops)]
  xt<-as.data.frame(model.matrix(~ . + 0, data=dataset, contrasts.arg = lapply(dataset, contrasts, contrasts=FALSE)))
  return(xt)
}
```
Remove Unwanted Columns
```{r}
rm.unwanted.col<-function(dataframe,cols){
  return(dataframe[-match(cols,names(dataframe))])
}
```
Load dataset Interface
```{r}
load.datasets<-function(){
  column.names <- c("TID","Bread","Milk","Diapers","Beer","Eggs","Cola")
  t1 <- c(1,1,1,0,0,0,0)
  t2 <- c(2,1,0,1,1,1,0)
  t3 <- c(3,1,1,1,1,0,1)
  t4 <- c(4,1,1,1,1,0,0)
  t5 <- c(5,1,1,1,0,0,1)

  data.mb<<- rbind(t1,t2,t3,t4,t5)
  data.mb <<- as.data.frame(data.mb)
  colnames(data.mb)<<-column.names
  data.mb<<-rm.unwanted.col(data.mb,"TID")
  
  nursery.data<- read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/nursery/nursery.data", header = FALSE,sep = ",",fill = TRUE)
  nursery.b<<-binarize(nursery.data,c( "parents","has_nurs","form","children","housing","finance","social","health"))
  
  car.data<- read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/car/car.data",header = FALSE,sep = ",", fill = TRUE)
  car.b<<-binarize(car.data,c("buying", "maint","doors","persons","lug_boot","safety"))
  
  tictac.data<-read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/tic-tac-toe/tic-tac-toe.data",header = FALSE,sep = ",", fill = TRUE)
  tictac.b<<-binarize(tictac.data,c("top-left-square","top-middle-square","top-right-square","middle-left-square",
                    "middle-middle-square","middle-right-square","bottom-left-square","bottom-middle-square","bottom-right-square","Class")
)
}

load.datasets()
```
Do Permutations and return a new dataset of itemsets
```{r}
permute.k.itemset<- function(itemset,k){
  cols<-as.vector(itemset$items)
  permutations(length(cols),k,cols)
}
```
FK-1 X F1 Method for Candidate Generation
```{r}
fkf1.candidate.gen<- function(col.set1,col.set2,k){
  cart.prod<- expand.grid(col.set1,col.set2)
  return(helper(cart.prod,k))
}
```
FK-1 X FK-1 Method for Candidate Generation
```{r}
fkfk.candidate.gen<-function(col.set1,col.set2,k){
  if(k == 2){
    return(fkf1.candidate.gen(col.set1,col.set2,k))
  }else{
    df<-data.frame(do.call('rbind', strsplit(as.character(col.set1)," "))) #fixed = TRUE was removed.
    df<- merge(df, df, by=names(df)[-(k-1)])
    return(helper(df,k))
  }
}
```
Helper function for two candidate generation method
```{r}
helper<-function(cart.prod,k){
    cart.prod<-mdply(cart.prod,paste)
    cart.prod<-cart.prod[,ncol(cart.prod)]
    table<-c()
  for(each_value in 1:length(cart.prod)){
    split.string <- unlist(strsplit(as.character(cart.prod[each_value]),split=" "))
    len<-length(unique(split.string))
    if(len == k){
      table<- rbind(table,paste(sort(split.string),collapse = " "))
    }
  }
  if(!is.null(table)){
    table<-remove.duplicates(as.data.frame(table))
  }
  return(table)  
}

```
Removing the duplicates
```{r}
remove.duplicates<-function(table){
   df<-data.frame(do.call('rbind', strsplit(as.character(table$V1)," ",fixed=TRUE)))
   return(as.matrix(mdply(df[!duplicated(t(apply(df, 1, sort))), ],paste)$V1))
}
```
Splitting Rules
```{r}
split <- function(lhs){
  s.vector <- c(unlist(strsplit(lhs,split = " ")))
  return(s.vector)
}

```
Rules Union Function
```{r}
rules.union <- function(lhs,rhs){
  union <- unique(c(split(lhs),split(rhs)))
  return(union)
}

```
Find Support
```{r}
Support <- function(dataset,columns,n){
  return(support.count(dataset,columns)/n)
}
```
Find Support Count
```{r}
support.count<-function(itemset,columns){
  subset <- select(itemset,match(columns,names(itemset)))
  for(column in columns){
    subset <- filter(subset,subset[column] == 1)
  }
  return(nrow(subset))
}

```
Find Confidence
```{r}
Confidence<-function(dataset,X,Y,n){
  x<-Support(dataset,rules.union(X,Y),n)
  y<-Support(dataset,X,n)
  return(x/y)
}

```
Find Lift
```{r}
lift<-function(dataset,X,Y,n){
  return(Confidence(dataset,X,Y,n)/Support(dataset,Y,n))
}
```
Frequent Item set Generation
```{r}
generate.frequent.itemsets<-function(dataset,columns,minsup,n,k){
  min.support.count <-  minsup * n
  items <- columns
  supports<- c()
  if(k == 1){ 
    for(each_column in columns){
      supports<- c(supports,support.count(dataset,each_column))
    }
  }else{
    items<-c()
    for(rownum in 1:nrow(columns)){
      supports<-c(supports,support.count(dataset,unlist(strsplit(as.character(columns[rownum,]),split = " "))))
      items<-c(items,as.character(paste(columns[rownum,],collapse = " ")))
    }
  }
  supports <- as.numeric(supports)
  candidate.itemset <- data.frame(items,supports)
  candidate.itemset <- filter(candidate.itemset,supports >= min.support.count)
  return(candidate.itemset)
}
```
Check for Empty Dataset
```{r}
is.Empty<- function(dataset){
  flag = FALSE
  if(is.data.frame(dataset)&& (nrow(dataset) == 0)){
    flag = TRUE
  }
  return(flag)
}
```
Apriori Algorithm
parameters: a binary dataset, Minimum support and method fk x f1 = "1" and fk-1 x fk-1 = "2"
```{r}
apriori.algorithm<-function(dataset,minsup = 0.5,method=1){
  k = 1
  number_of_candidate_itemset<<-0
  number_of_frequent_itemset<<-0
  dataset<-as.data.frame(dataset)
  f1 <- generate.frequent.itemsets(dataset,names(dataset),minsup,nrow(dataset),k)
  pander::pandoc.table(f1,style="grid",caption = paste("Frequent",1,"Item set ", "Number of Frequent Itemset: ",nrow(f1)) )
  Frequent.itemsets <-  data.frame(Frequent_itemset=as.character())
  if(nrow(f1) == 0){
    return()
  }
  Frequent.itemsets<- rbind(Frequent.itemsets, cbind(f1, minsup))
  number_of_frequent_itemset<<-c(number_of_frequent_itemset,nrow(f1))
  number_of_candidate_itemset<<-c(number_of_candidate_itemset,nrow(dataset))
  candidate.set<-as.matrix(f1$items)
  fk<-f1
    while(!is.Empty(fk)){
      k = k + 1
        if(method == 1){
          candidate.set<-fkf1.candidate.gen(fk$items,f1$items,k) 
        }else{
          candidate.set<-fkfk.candidate.gen(fk$items,fk$items,k) 
        }
        if(is.null(candidate.set)){ 
          break
        }
        pander::pandoc.table(candidate.set,style="grid",caption = paste("Candidate",k,"Item set ", "Number of Candidate Itemset:",nrow(candidate.set)) )
        number_of_candidate_itemset<<-c(number_of_candidate_itemset,nrow(candidate.set))
        
        fk<- generate.frequent.itemsets(dataset,candidate.set,minsup,nrow(dataset),k) #fk dataset
        if(!is.Empty(fk)){
          Frequent.itemsets<- rbind(Frequent.itemsets, cbind(fk, minsup))
        }
        pander::pandoc.table(fk,style="grid",caption = paste("Frequent",k,"Item set ", "Number of Frequent Itemset:",nrow(fk)) )
        number_of_frequent_itemset<<-c(number_of_frequent_itemset,nrow(fk))
    }
    return(list(c(nrow(dataset),sum(number_of_candidate_itemset),sum(number_of_frequent_itemset),minsup),Frequent.itemsets))
  }
```
Data set 1: Toy
```{r}
Toy.fkf1<- function(){
  #Execute Apriori Algorithm
  
  Toy.ob1<-apriori.algorithm(data.mb,minsup = 0.1,method = 1)[[1]]
  Toy.ob2<-apriori.algorithm(data.mb,minsup = 0.2,method = 1)[[1]]
  Toy.ob3<-apriori.algorithm(data.mb,minsup = 0.5,method = 1)[[1]]
  
  #Statistics
  tracking.statistics.table.fkf1 <<- data.frame(Size=as.numeric(),Candidate.items = as.numeric(),Frequent.items = as.numeric())
  tracking.statistics.table.fkf1 <<- rbind(Toy.ob1,Toy.ob2,Toy.ob3)
  colnames(tracking.statistics.table.fkf1)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")

}
```
Data set 2: Nursery : abnormal Issue with nursery.ob3, check before submission
```{r}
Nursery.fkf1<-function(){
  
  #Execute Apriori Algorithm
  nursery.ob1<-apriori.algorithm(nursery.b,minsup = 0.1,method = 1)[[1]]
  nursery.ob2<-apriori.algorithm(nursery.b,minsup = 0.2,method = 1)[[1]]
  nursery.ob3<-apriori.algorithm(nursery.b,minsup = 0.5,method = 1)[[1]]
  
  #Statistics
  tracking.statistics.table.fkf1 <<- rbind(tracking.statistics.table.fkf1,nursery.ob1,nursery.ob2,nursery.ob3)
  colnames(tracking.statistics.table.fkf1)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")
}
```
Data set 3 : Car
```{r}
Car.fkf1<-function(){
  #Execute Apriori Algorithm
  car.ob1<-apriori.algorithm(car.b,minsup = 0.1,method = 1)[[1]]
  car.ob2<-apriori.algorithm(car.b,minsup = 0.2,method = 1)[[1]]
  car.ob3<-apriori.algorithm(car.b,minsup = 0.5,method = 1)[[1]]
  
  #Statistics
  tracking.statistics.table.fkf1 <<- rbind(tracking.statistics.table.fkf1,car.ob1,car.ob2,car.ob3)
  colnames(tracking.statistics.table.fkf1)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")
}
```
Dataset 4 : Tic-Tac-Toe
```{r}
Tictac.fkf1<-function(){
  #Execute Apriori Algorithm
  tictac.ob1<-apriori.algorithm(tictac.b,minsup = 0.1,method = 1)[[1]]
  tictac.ob2<-apriori.algorithm(tictac.b,minsup = 0.2,method = 1)[[1]]
  tictac.ob3<-apriori.algorithm(tictac.b,minsup = 0.5,method = 1)[[1]]
  
  #Statistics
  tracking.statistics.table.fkf1 <<- rbind(tracking.statistics.table.fkf1,tictac.ob1,tictac.ob2,tictac.ob3)
  colnames(tracking.statistics.table.fkf1)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")
}

```
Apriori Fk-1 x F1
```{r}
Toy.fkf1()
Nursery.fkf1()
Car.fkf1()
Tictac.fkf1()
#Prints the table
tracking.statistics.table.fkf1
```
Data set 1 : Toy
```{r}

Toy.fkfk<- function(){
  
  #Execute Apriori Algorithm
  Toy.ob1<-apriori.algorithm(data.mb,minsup = 0.1,method = 2)[[1]]
  Toy.ob2<-apriori.algorithm(data.mb,minsup = 0.2,method = 2)[[1]]
  Toy.ob3<-apriori.algorithm(data.mb,minsup = 0.5,method = 2)[[1]]
  
  #Statistics
  tracking.statistics.table.fkfk <<- data.frame(Size=as.numeric(),Candidate.items = as.numeric(),Frequent.items = as.numeric())
  tracking.statistics.table.fkfk <<- rbind(Toy.ob1,Toy.ob2,Toy.ob3)
  colnames(tracking.statistics.table.fkfk)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")
}

```
Data set 2: Nursery
```{r}
Nursery.fkfk<-function(){
  
  #Execute Apriori Algorithm
  nursery.ob1<-apriori.algorithm(nursery.b,minsup = 0.1,method = 2)[[1]]
  nursery.ob2<-apriori.algorithm(nursery.b,minsup = 0.2,method = 2)[[1]]
  nursery.ob3<-apriori.algorithm(nursery.b,minsup = 0.5,method = 2)[[1]]
  
  #Statistics
  tracking.statistics.table.fkfk <<- rbind(tracking.statistics.table.fkfk,nursery.ob1,nursery.ob2,nursery.ob3)
  colnames(tracking.statistics.table.fkfk)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")
 
}
```
Data set 3: Car
```{r}
Car.fkfk<-function(){
  
  #Execute Apriori Algorithm
  car.ob1<-apriori.algorithm(car.b,minsup = 0.1,method = 2)[[1]]
  car.ob2<-apriori.algorithm(car.b,minsup = 0.2,method = 2)[[1]]
  car.ob3<-apriori.algorithm(car.b,minsup = 0.5,method = 2)[[1]]
  
  #Statistics
  tracking.statistics.table.fkfk <<- rbind(tracking.statistics.table.fkfk,car.ob1,car.ob2,car.ob3)
  colnames(tracking.statistics.table.fkfk)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")
}
```
Dataset 4 : Tic-Tac-Toe
```{r}
Tictac.fkfk<-function(){
  #Execute Apriori Algorithm
  tictac.ob1<-apriori.algorithm(tictac.b,minsup = 0.1,method = 2)[[1]]
  tictac.ob2<-apriori.algorithm(tictac.b,minsup = 0.2,method = 2)[[1]]
  tictac.ob3<-apriori.algorithm(tictac.b,minsup = 0.5,method = 2)[[1]]
  
  #Statistics
  tracking.statistics.table.fkfk <<- rbind(tracking.statistics.table.fkfk,tictac.ob1,tictac.ob2,tictac.ob3)
  colnames(tracking.statistics.table.fkfk)<<-c("Size","Candidate Itemset","Frequent Itemset","Support")
}
```
Apriori Fk-1 x Fk
```{r}
Toy.fkfk()
Nursery.fkfk()
Car.fkfk()
Tictac.fkfk()

#Prints the table
tracking.statistics.table.fkfk
```
Make Frequent Itemset Available globally
```{r}
SetGlobalVariable.Frequent.itemset<-function(dataset1,dataset2,dataset3,dataset4){
  
  Toy.fqi1<<-apriori.algorithm(dataset1,minsup = 0.1,method = 2)[[2]]
  Toy.fqi2<<-apriori.algorithm(dataset1,minsup = 0.2,method = 2)[[2]]
  Toy.fqi3<<-apriori.algorithm(dataset1,minsup = 0.5,method = 2)[[2]]
  
  Nursery.fqi1<<-apriori.algorithm(dataset2,minsup = 0.1,method = 2)[[2]]
  Nursery.fqi2<<-apriori.algorithm(dataset2,minsup = 0.2,method = 2)[[2]]
  Nursery.fqi3<<-apriori.algorithm(dataset2,minsup = 0.5,method = 2)[[2]]
    
  Car.fqi1<<-apriori.algorithm(dataset3,minsup = 0.1,method = 2)[[2]]
  Car.fqi2<<-apriori.algorithm(dataset3,minsup = 0.2,method = 2)[[2]]
  Car.fqi3<<-apriori.algorithm(dataset3,minsup = 0.5,method = 2)[[2]]
  
  Tictac.fqi1<<-apriori.algorithm(dataset4,minsup = 0.1,method = 2)[[2]]
  Tictac.fqi2<<-apriori.algorithm(dataset4,minsup = 0.2,method = 2)[[2]]
  Tictac.fqi3<<-apriori.algorithm(dataset4,minsup = 0.5,method = 2)[[2]]
}
```
Create Frequent itemsets globally for further analysis
```{r}
SetGlobalVariable.Frequent.itemset(data.mb,nursery.b,car.b,tictac.b)
```
Some Plots
```{r}
trackfkf1<-as.data.frame(tracking.statistics.table.fkf1)
trackfkfk<-as.data.frame(tracking.statistics.table.fkfk)

#"Fk - 1 x F1"
qplot(Size, `Candidate Itemset`,data = trackfkf1, color = Support, size = 2, main = "Size vs Candidate Itemset (Fk-1 x F1)")
qplot(Size, `Frequent Itemset`, data = trackfkf1, color = Support, size = 2, main = "Size vs Frequent Itemset (Fk-1 x F1)")

#"Fk - 1 x Fk-1"
qplot(Size, `Candidate Itemset`,data = trackfkfk, color = Support, size = 2, main = "Size vs Candidate Itemset (Fk-1 x Fk-1)")
qplot(Size, `Frequent Itemset`, data = trackfkfk, color = Support, size = 2, main = "Size vs Frequent Itemset (Fk-1 x Fk-1)")

```
Maximal Frequent Itemset
```{r}
maximal.freq.itemset<- function(frequent.itemsets){
  x<- as.vector(frequent.itemsets$items)
  minsup<- unique(frequent.itemsets$minsup)
  flag = FALSE
  max.item<-c()
  for(i in 1:nrow(frequent.itemsets)){
    s1<- unlist(strsplit(as.character(x[i]),split = " "))
    for(j in 1:nrow(frequent.itemsets)){
      s2<- unlist(strsplit(as.character(x[j]), split = " "))
      if(length(s1) == length(s2)){
        break
      }
      if(all(s1 %in% s2) && length(s2) > length(s1)){  # && !(length(s2)<length(s1)+2)
        flag = FALSE
        break
      }else{
        flag = TRUE
      }
    }
    if(flag == TRUE){
      max.item<- c(max.item,paste(sort(s1),collapse = " "))
    }
  }
  return(max.item)
}
```
Closed Frequent Itemset
```{r}
closed.frequent.itemset<- function(dataset, minsup){
  power.set<-findPowerset(names(dataset))
  lattice<-c()
  closed.item<-c()
  for(row in 1:length(power.set)){
    if(length(power.set[[row]]) == 0){
      next
    }
    lattice<- rbind(lattice,cbind(paste(sort(power.set[[row]]),collapse = " "), as.integer(support.count(dataset,(unlist(power.set[[row]]))))))
  }
  lattice<- as.data.frame(lattice)
  colnames(lattice)<- c("Itemset","Support")
  x<-lattice$Itemset
  y<-lattice$Support
  flag<-FALSE
  for(i in 1:nrow(lattice)){
    s1<- unlist(strsplit(as.character(x[i]),split = " "))
    s1.sup<- as.numeric(as.character(y[i]))
    for(j in 1:nrow(lattice)){
      s2<- unlist(strsplit(as.character(x[j]), split = " "))
      s2.sup <- as.numeric(as.character(y[j]))
      if(length(s2) == length(s1) + 1){
        if(all(s1 %in% s2)){
          if(s2.sup != s1.sup){
            flag = TRUE
          }else{
            flag = FALSE
            break
          }
        }
      }
       
    }
    if(s1.sup < (nrow(dataset) * minsup)){
          flag = FALSE
        }
    if(flag == TRUE){
      closed.item<- c(closed.item,paste(sort(s1),collapse = " "))
    }
  }
  return(closed.item)
}
```
Calculate Power set :- Code taken from stackoverflow (http://stackoverflow.com/questions/18715580/algorithm-to-calculate-power-set-all-possible-subsets-of-a-set-in-r)
```{r}
findPowerset<- function(set){
  n <- length(set)
  keepBool <- sapply(2^(1:n - 1), function(k) 
    rep(c(FALSE, TRUE), each=k, times=(2^n / (2*k))))
  lapply(1:2^n, function(j) set[keepBool[j, ]])
}

```
Finding Close Item set and Maximal Itemset Interface
```{r}
ClosedAndMaximal<-function(){
  cat(paste("Maximal Frequent Itemset:Support: 0.1"))
  toy1<-length(maximal.freq.itemset(Toy.fqi1))
  cat(paste("Maximal Frequent Itemset:Support: 0.2"))
  toy2<-length(maximal.freq.itemset(Toy.fqi2))
  cat(paste("Maximal Frequent Itemset:Support: 0.5"))
  toy3<-length(maximal.freq.itemset(Toy.fqi3))
  
  cat(paste("Maximal Frequent Itemset:Support: 0.1"))
  nursery1<-length(maximal.freq.itemset(Nursery.fqi1))
  cat(paste("Maximal Frequent Itemset:Support: 0.2"))
  nursery2<-length(maximal.freq.itemset(Nursery.fqi2))
  cat(paste("Maximal Frequent Itemset:Support: 0.5"))
  nursery3<-length(maximal.freq.itemset(Nursery.fqi3))
  
  cat(paste("Maximal Frequent Itemset:Support: 0.1"))
  car1<-length(maximal.freq.itemset(Car.fqi1))
  cat(paste("Maximal Frequent Itemset:Support: 0.2"))
  car2<-length(maximal.freq.itemset(Car.fqi2))
  
  cat(paste("Maximal Frequent Itemset:Support: 0.1"))
  tictac1<-length(maximal.freq.itemset(Tictac.fqi1))
  cat(paste("Maximal Frequent Itemset:Support: 0.2"))
  tictac2<-length(maximal.freq.itemset(Tictac.fqi2))
  cat(paste("Maximal Frequent Itemset:Support: 0.5"))
  tictac3<-length(maximal.freq.itemset(Tictac.fqi3))
  
  
  cat(paste("Closed Frequent Itemset:Support: 0.1"))
  toy1.c<-length(closed.frequent.itemset(data.mb,0.1))
  cat(paste("Closed Frequent Itemset:Support: 0.2"))
  toy2.c<-length(closed.frequent.itemset(data.mb,0.2))
  cat(paste("Closed Frequent Itemset:Support: 0.5"))
  toy3.c<-length(closed.frequent.itemset(data.mb,0.5))
  
  cat(paste("Closed Frequent Itemset:Support: 0.1"))
  closed.frequent.itemset(nursery.b,0.1)
  cat(paste("Closed Frequent Itemset:Support: 0.2"))
  closed.frequent.itemset(nursery.b,0.2)
  cat(paste("Closed Frequent Itemset:Support: 0.5"))
  closed.frequent.itemset(nursery.b,0.5)
  
  cat(paste("Closed Frequent Itemset:Support: 0.1"))
  car1.c<-length(closed.frequent.itemset(car.b,0.1))
  cat(paste("Closed Frequent Itemset:Support: 0.2"))
  car2.c<-length(closed.frequent.itemset(car.b,0.2))
  cat(paste("Closed Frequent Itemset:Support: 0.5"))
  car3.c<-length(closed.frequent.itemset(car.b,0.5))
  
  cat(paste("Closed Frequent Itemset:Support: 0.1"))
  nursery1.c<-length(closed.frequent.itemset(nursery.b,0.1))
  cat(paste("Closed Frequent Itemset:Support: 0.2"))
  nursery2.c<-length(closed.frequent.itemset(nursery.b,0.2))
  cat(paste("Closed Frequent Itemset:Support: 0.5"))
  nursery3.c<-length(closed.frequent.itemset(nursery.b,0.5))
  
  
  cat(paste("Maximal Frequent Itemset:Support: 0.1"))
  tictac1.c<-length(closed.frequent.itemset(tictac.b,0.1))
  cat(paste("Maximal Frequent Itemset:Support: 0.2"))
  tictac2.c<-length(closed.frequent.itemset(tictac.b,0.2))
  cat(paste("Maximal Frequent Itemset:Support: 0.5"))
  tictac3.c<-tictac1.c<-length(closed.frequent.itemset(tictac.b,0.5))
  
  toy1m<- cbind("Toy",toy1,toy1.c)
  toy2m<- cbind("Toy",toy2,toy2.c)
  toy3m<- cbind("Toy",toy3,toy3.c)
  
  nursery1m<- cbind("Nursery",nursery1,nursery1.c)
  nursery2m<- cbind("Nursery",nursery2,nursery2.c)
  nursery3m<- cbind("Nursery",nursery3,nursery3.c)
  
  car1m<- cbind(car1,car1.c)
  car2m<- cbind(car2,car2.c)
  car3m<- cbind(0,car3.c)
  
  tictac1m<- cbind("TictacToe",tictac1,tictac1.c)
  tictac2m<- cbind("TictacToe",tictac2,tictac2.c)
  tictac3m<- cbind("TictacToe",tictac3,tictac3.c)
  
  close.freq.table<<-as.data.frame(rbind(toy1m,toy2m,toy3m,nursery1m,nursery2m,nursery3m,car1m,car2m,tictac1m,tictac2m,tictac3m))
  return(t)
}

```
Rule Generation and pruning using Confidence and Lift
```{r}
rule.gen<- function(dataset,frequent.itemsets, threshold,prune_by){
  items<- frequent.itemsets$items
  prune_subsets<-c()
  countRules<<- 0
  bruteForce<<-0
  rules.lift.table<<-data.frame(Rules=as.character(character()),
                 Lift=numeric(0), 
                 stringsAsFactors=FALSE)
  rules.conf.table<<-data.frame(Rules=as.character(character()),
                 Confidence=numeric(0), 
                 stringsAsFactors=FALSE) 
  for(i in 1:length(items)){
    split.item<- unlist(strsplit(as.character(items[i]),split = " "))
    pwset<- findPowerset(split.item)
    bruteForce<<- bruteForce + length(split.item)
    for(j in 1:length(pwset)){
      sub.pwset<- pwset[[j]]
      if(length(sub.pwset)>0){
        X = sub.pwset
        Y = setdiff(split.item,X)
        if(all(X %in% prune_subsets)){
          break
        }
        if(length(X) != 0 && length(Y) !=0){
          if(prune_by == "confidence"){
            conf <- Confidence(dataset,X,Y,nrow(dataset))
            if(conf< threshold){
              prune_subsets_of<-unique(c(prune_subsets,X))
              break
            }
            rules.conf.table<<-as.data.frame(rbind(rules.conf.table,cbind.data.frame(Rules =paste(paste(X, collapse = " "), "=>",paste(Y, collapse = " ")),conf)))
            countRules <<- countRules + 1
          }else if(prune_by == "lift"){
            l <- lift(dataset,X,Y,nrow(dataset))
            if(l< threshold){
              prune_subsets_of<-unique(c(prune_subsets,X))
              break
            }
            rules.lift.table<<-as.data.frame(rbind(rules.lift.table,cbind.data.frame(Rules =paste(paste(X, collapse = " "), "=>",paste(Y, collapse = " ")),l)))
            countRules<<- countRules + 1
          }
          
        }
      }
      
    }
  }
}
```
Show Top Ten Rules using confidence
```{r}
topTenConf<-function(){
  conf1<- 0.3
  conf2<- 0.4
  conf3<- 0.6
  ############ Toy ###########
  cat("Support: 0.1")
  cat(paste("Top ten: Toy, Confidence = conf1","\n\n\n"))
  rule.gen(data.mb,Toy.fqi1,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Toy, Confidence = conf2","\n\n\n"))
  rule.gen(data.mb,Toy.fqi1,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Toy, Confidence = conf3"),"\n\n\n")
  rule.gen(data.mb,Toy.fqi1,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Toy, Confidence = conf1","\n\n\n"))
  rule.gen(data.mb,Toy.fqi2,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Toy, Confidence = conf2","\n\n\n"))
  rule.gen(data.mb,Toy.fqi2,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Toy, Confidence = conf3"),"\n\n\n")
  rule.gen(data.mb,Toy.fqi2,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat("Support: 0.5")
  cat(paste("Top ten: Toy, Confidence = conf1","\n\n\n"))
  rule.gen(data.mb,Toy.fqi3,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Toy, Confidence = conf2","\n\n\n"))
  rule.gen(data.mb,Toy.fqi3,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Toy, Confidence = conf3"),"\n\n\n")
  rule.gen(data.mb,Toy.fqi3,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  
  ####### NUrsery ########
  cat("Support: 0.1")
  cat(paste("Top ten: Nursery, Confidence = conf1","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi1,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Nursery, Confidence = conf2","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi1,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Nursery, Confidence = conf3"),"\n\n\n")
  rule.gen(nursery.b,Nursery.fqi1,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Nursery, Confidence = conf1","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi2,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Nursery, Confidence = conf2","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi2,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Nursery, Confidence = conf3"),"\n\n\n")
  rule.gen(nursery.b,Nursery.fqi2,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat("Support: 0.5")
  cat(paste("Top ten: Nursery, Confidence = conf1","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi3,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Nursery, Confidence = conf2","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi3,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Nursery, Confidence = conf3"),"\n\n\n")
  rule.gen(nursery.b,Nursery.fqi3,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  ######### Car #########
  
  cat("Support: 0.1")
  cat(paste("Top ten: Nursery, Confidence = conf1","\n\n\n"))
  rule.gen(car.b,Car.fqi1,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Car, Confidence = conf2","\n\n\n"))
  rule.gen(car.b,Car.fqi1,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Car, Confidence = conf3"),"\n\n\n")
  rule.gen(car.b,Car.fqi1,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Car, Confidence = conf1","\n\n\n"))
  rule.gen(car.b,Car.fqi2,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Car, Confidence = conf2","\n\n\n"))
  rule.gen(car.b,Car.fqi2,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Car, Confidence = conf3"),"\n\n\n")
  rule.gen(car.b,Car.fqi2,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  ######## Tic-Tac-Toe ###########
  
  cat("Support: 0.1")
  cat(paste("Top ten: Nursery, Confidence = conf1","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi1,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, Confidence = conf2","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi1,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, Confidence = conf3"),"\n\n\n")
  rule.gen(tictac.b,Tictac.fqi1,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.1,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Tic Tac Toe, Confidence = conf1","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi2,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, Confidence = conf2","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi2,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, Confidence = conf3"),"\n\n\n")
  rule.gen(tictac.b,Tictac.fqi2,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.2,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat("Support: 0.5")
  cat(paste("Top ten: Tic Tac Toe, Confidence = conf1","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi3,conf1,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.3)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, Confidence = conf2","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi3,conf2,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.4)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, Confidence = conf3"),"\n\n\n")
  rule.gen(tictac.b,Tictac.fqi3,conf3,"confidence")
  conf.brute.tables<<- as.data.frame(rbind(conf.brute.tables, cbind(paste("2^",bruteForce-1),countRules,0.5,0.6)))
  print(arrange(rules.conf.table, desc(conf))[1:10,])
  
  
}

topTenConf()
```
Show top 10 Rules using lift
```{r}

topTenLift<-function(){
  
  
  ############ Toy ###########
  cat("Support: 0.1")
  cat(paste("Top ten: Toy, lift = 0.5","\n\n\n"))
  rule.gen(data.mb,Toy.fqi1,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Toy, lift = 0.7","\n\n\n"))
  rule.gen(data.mb,Toy.fqi1,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Toy, lift = 0.9"),"\n\n\n")
  rule.gen(data.mb,Toy.fqi1,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Toy, lift = 0.5","\n\n\n"))
  rule.gen(data.mb,Toy.fqi2,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Toy, lift = 0.7","\n\n\n"))
  rule.gen(data.mb,Toy.fqi2,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Toy, lift = 0.9"),"\n\n\n")
  rule.gen(data.mb,Toy.fqi2,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat("Support: 0.5")
  cat(paste("Top ten: Toy, lift = 0.5","\n\n\n"))
  rule.gen(data.mb,Toy.fqi3,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Toy, lift = 0.7","\n\n\n"))
  rule.gen(data.mb,Toy.fqi3,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Toy, lift = 0.9"),"\n\n\n")
  rule.gen(data.mb,Toy.fqi3,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  
  
  ####### NUrsery ########
  cat("Support: 0.1")
  cat(paste("Top ten: Nursery, lift = 0.5","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi1,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Nursery, lift = 0.7","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi1,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Nursery, lift = 0.9"),"\n\n\n")
  rule.gen(nursery.b,Nursery.fqi1,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Nursery, lift = 0.5","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi2,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Nursery, lift = 0.7","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi2,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Nursery, lift = 0.9"),"\n\n\n")
  rule.gen(nursery.b,Nursery.fqi2,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat("Support: 0.5")
  cat(paste("Top ten: Nursery, lift = 0.5","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi3,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Nursery, lift = 0.7","\n\n\n"))
  rule.gen(nursery.b,Nursery.fqi3,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Nursery, lift = 0.9"),"\n\n\n")
  rule.gen(nursery.b,Nursery.fqi3,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  ######### Car #########
  
  cat("Support: 0.1")
  cat(paste("Top ten: Nursery, lift = 0.5","\n\n\n"))
  rule.gen(car.b,Car.fqi1,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Car, lift = 0.7","\n\n\n"))
  rule.gen(car.b,Car.fqi1,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Car, lift = 0.9"),"\n\n\n")
  rule.gen(car.b,Car.fqi1,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Car, lift = 0.5","\n\n\n"))
  rule.gen(car.b,Car.fqi2,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Car, lift = 0.7","\n\n\n"))
  rule.gen(car.b,Car.fqi2,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Car, lift = 0.9"),"\n\n\n")
  rule.gen(car.b,Car.fqi2,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  ######## Tic-Tac-Toe ###########
  
  cat("Support: 0.1")
  cat(paste("Top ten: Nursery, lift = 0.5","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi1,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, lift = 0.7","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi1,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, lift = 0.9"),"\n\n\n")
  rule.gen(tictac.b,Tictac.fqi1,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat("Support: 0.2")
  cat(paste("Top ten: Tic Tac Toe, lift = 0.5","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi2,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, lift = 0.7","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi2,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, lift = 0.9"),"\n\n\n")
  rule.gen(tictac.b,Tictac.fqi2,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat("Support: 0.5")
  cat(paste("Top ten: Tic Tac Toe, lift = 0.5","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi3,0.5,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, lift = 0.7","\n\n\n"))
  rule.gen(tictac.b,Tictac.fqi3,0.7,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  cat(paste("\nTop ten: Tic Tac Toe, lift = 0.9"),"\n\n\n")
  rule.gen(tictac.b,Tictac.fqi3,0.9,"lift")
  print(arrange(rules.lift.table, desc(l))[1:10,])
  
  
}

topTenLift()
```



